---
title: "Predictive Loan"
output: html_document
date: "2023-10-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries

```{r}
library(tidyverse)
library(dplyr)
library(stringr)
```

## Call in DataFrame

```{r}
df_overview <- read_csv('~/Documents/GitHub/tableau_Fri_project/loan_shark.csv')
df_overview
```

## Change DataFrame into Tibble

```{r}
tibble_overview <- as_tibble(df_overview)
View(df_overview)
```

## Cleaning DataFrame

```{r}
#cleaning column names

rename_cols <- function(df_overview) {
  #retrieve the column names using names(x)
  names(df_overview) <- names(df_overview) %>% str_replace_all('\\.', '')%>% tolower()
  return(df_overview)
}

df_overview <- rename_cols(df_overview)
view(df_overview)
```

```{r}
#adding '_' to some column names
colnames(df_overview)[1] ="num"
colnames(df_overview)[8] ="applicant_income"
colnames(df_overview)[9] ="co_applicant_income"
colnames(df_overview)[10] ="loan_amount"

view(df_overview)
```

```{r}
# dropping column

df_overview2 = select(df_overview, -1,-7)
#df_overview2 = select(df_overview, -)

view(df_overview2)
```

### Converting to CSV file for further cleaning in Python

```{r}
#converting to CSV file for further cleaning in Python
write.csv(df_overview2,file='loandata_version2.csv',na='')
```

## Calling in csv cleaned in python

```{r}
df_overview3 <- read_csv('~/Documents/GitHub/Capstone1_Data_Insights_for_Loan_DEI/new_clean_loan.csv')
df_overview3
```

## Further cleaning

```{r}
#dropping columns
df_overview4 <- df_overview3[-c(1,2)]
view(df_overview4)
```

## Exporting completed clean file

```{r}
write.csv(df_overview4,file='loandata_finalversion.csv')
```

## Visulization

```{r}
ggplot(df_overview4) +
  geom_point(aes(x = gender, y = loan_amount)) +
  labs(title = "Comparison of gender and loan_amount", x = "Gender", y = "Loan_amount")
```

```{r}
ggplot(df_overview4) +
  geom_point(aes(x = dependents, y = loan_amount)) +
  labs(title = "Comparison of dependents and loan_amount", x = "dependents", y = "Loan_amount")
```

# Statistical Testing

```{r}

t.test(df_overview4['dependents'], df_overview4['loan_amount'])
```

## Interpretation:

The p-value \< 2.2e-16, is scientific notation for the equivalent of p \< .00000000000000016. Therefore, we can conclude conclude that there is a significant (positive) relationship between dependents, and loan amount dispersion.
